Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-04 paper/AlignedIsotropicGW.tex
Punctuation fix.

In Table~\ref{tab:accumulation} we show how the evidence for an isotropic distribution increases when including; only the 2 confirmed events---GW150914 and GW151226---from O1; all O1 events (including LVT151012); and all 4 likely binary black hole mergers, including GW170104.

>>>>

In Table~\ref{tab:accumulation} we show how the evidence for an isotropic distribution increases when including: only the 2 confirmed events---GW150914 and GW151226---from O1; all O1 events (including LVT151012); and all 4 likely binary black hole mergers, including GW170104.
